---
title: "NEW Age Negative batch correction and stats hippocampus"
output: html_document
date: "2023-08-14"
---

# Install Packages 

```{r}
library(maplet)
library(magrittr)
library(dplyr)
library(tidyverse)
library(car)
library(data.table)
require(plyr)
#install.packages('ggpubr')
library(ggpubr)
```

# Import Data and normalize brains percentage to pixel sizes

Below we import the data.

```{r}
percentage_of_ion_intensities_roi_226_a2_wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/226_a2_wt_s2_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_226_a2_wt_hippocampus_df)[1] = "226_a2_wt"
# Make row names into column
percentage_of_ion_intensities_roi_226_a2_wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_226_a2_wt_hippocampus_df)

percentage_of_ion_intensities_roi_225_4wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/225_4wt_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_225_4wt_hippocampus_df)[1] = "225_4wt"
# Make row names into column
percentage_of_ion_intensities_roi_225_4wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_225_4wt_hippocampus_df)

percentage_of_ion_intensities_roi_225_a1wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/225_a1wt_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_225_a1wt_hippocampus_df)[1] = "225_a1wt"
# Make row names into column
percentage_of_ion_intensities_roi_225_a1wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_225_a1wt_hippocampus_df)

percentage_of_ion_intensities_roi_208_5wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/208_5wt_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_208_5wt_hippocampus_df)[1] = "208_5wt"
# Make row names into column
percentage_of_ion_intensities_roi_208_5wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_208_5wt_hippocampus_df)

percentage_of_ion_intensities_roi_209_2wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/209_2wt_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_209_2wt_hippocampus_df)[1] = "209_2wt"
# Make row names into column
percentage_of_ion_intensities_roi_209_2wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_209_2wt_hippocampus_df)

percentage_of_ion_intensities_roi_278_a2_wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/278_a2_wt_s1_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_278_a2_wt_hippocampus_df)[1] = "278_a2_wt"
# Make row names into column
percentage_of_ion_intensities_roi_278_a2_wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_278_a2_wt_hippocampus_df)

percentage_of_ion_intensities_roi_191_a3wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/191_a3wt_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_191_a3wt_hippocampus_df)[1] = "191_a3wt"
# Make row names into column
percentage_of_ion_intensities_roi_191_a3wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_191_a3wt_hippocampus_df)

percentage_of_ion_intensities_roi_252_8_wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/252_8_wt_s1_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_252_8_wt_hippocampus_df)[1] = "252_8_wt"
# Make row names into column
percentage_of_ion_intensities_roi_252_8_wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_252_8_wt_hippocampus_df)

percentage_of_ion_intensities_roi_268_a3_wt_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/268_a3_wt_s2_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_268_a3_wt_hippocampus_df)[1] = "268_a3_wt"
# Make row names into column
percentage_of_ion_intensities_roi_268_a3_wt_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_268_a3_wt_hippocampus_df)

percentage_of_ion_intensities_roi_225_a2tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/225_a2tg_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_225_a2tg_hippocampus_df)[1] = "225_a2tg"
# Make row names into column
percentage_of_ion_intensities_roi_225_a2tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_225_a2tg_hippocampus_df)

percentage_of_ion_intensities_roi_270_5_Tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/270_5_Tg_s4_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_270_5_Tg_hippocampus_df)[1] = "270_5_Tg"
# Make row names into column
percentage_of_ion_intensities_roi_270_5_Tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_270_5_Tg_hippocampus_df)

percentage_of_ion_intensities_roi_225_3tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/225_3tg_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_225_3tg_hippocampus_df)[1] = "225_3tg"
# Make row names into column
percentage_of_ion_intensities_roi_225_3tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_225_3tg_hippocampus_df)

percentage_of_ion_intensities_roi_270_a1_Tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/270_a1_Tg_s1_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_270_a1_Tg_hippocampus_df)[1] = "270_a1_Tg"
# Make row names into column
percentage_of_ion_intensities_roi_270_a1_Tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_270_a1_Tg_hippocampus_df)

percentage_of_ion_intensities_roi_226_a1tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/226_a1tg_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_226_a1tg_hippocampus_df)[1] = "226_a1tg"
# Make row names into column
percentage_of_ion_intensities_roi_226_a1tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_226_a1tg_hippocampus_df)

percentage_of_ion_intensities_roi_210_a1tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/210_a1tg_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_210_a1tg_hippocampus_df)[1] = "210_a1tg"
# Make row names into column
percentage_of_ion_intensities_roi_210_a1tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_210_a1tg_hippocampus_df)

percentage_of_ion_intensities_roi_249_4_Tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/249_4_Tg_s1_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_249_4_Tg_hippocampus_df)[1] = "249_4_Tg"
# Make row names into column
percentage_of_ion_intensities_roi_249_4_Tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_249_4_Tg_hippocampus_df)

percentage_of_ion_intensities_roi_256_a3_Tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/256_a3_Tg_s1_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_256_a3_Tg_hippocampus_df)[1] = "256_a3_Tg"
# Make row names into column
percentage_of_ion_intensities_roi_256_a3_Tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_256_a3_Tg_hippocampus_df)

percentage_of_ion_intensities_roi_268_3_Tg_hippocampus_df <- read.csv('D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/268_3_Tg_s4_percentage_of_ions_within_hippocampus.csv', row.names = 1)
# Rename column
colnames(percentage_of_ion_intensities_roi_268_3_Tg_hippocampus_df)[1] = "268_3_Tg"
# Make row names into column
percentage_of_ion_intensities_roi_268_3_Tg_hippocampus_df$ions <- rownames(percentage_of_ion_intensities_roi_268_3_Tg_hippocampus_df)
```

Below we combine all the normalized percentage.

```{r}
dfs_to_merge <- list(percentage_of_ion_intensities_roi_226_a2_wt_hippocampus_df, percentage_of_ion_intensities_roi_225_4wt_hippocampus_df, percentage_of_ion_intensities_roi_225_a1wt_hippocampus_df, percentage_of_ion_intensities_roi_208_5wt_hippocampus_df, percentage_of_ion_intensities_roi_209_2wt_hippocampus_df, percentage_of_ion_intensities_roi_278_a2_wt_hippocampus_df, percentage_of_ion_intensities_roi_191_a3wt_hippocampus_df, percentage_of_ion_intensities_roi_252_8_wt_hippocampus_df, percentage_of_ion_intensities_roi_268_a3_wt_hippocampus_df, percentage_of_ion_intensities_roi_225_a2tg_hippocampus_df, percentage_of_ion_intensities_roi_270_5_Tg_hippocampus_df, percentage_of_ion_intensities_roi_225_3tg_hippocampus_df, percentage_of_ion_intensities_roi_270_a1_Tg_hippocampus_df, percentage_of_ion_intensities_roi_226_a1tg_hippocampus_df, percentage_of_ion_intensities_roi_210_a1tg_hippocampus_df, percentage_of_ion_intensities_roi_249_4_Tg_hippocampus_df, percentage_of_ion_intensities_roi_256_a3_Tg_hippocampus_df, percentage_of_ion_intensities_roi_268_3_Tg_hippocampus_df)
# Merge all into one
final_data_merged <- dfs_to_merge %>% reduce(full_join, by='ions')
# make ions into rownames again
rownames(final_data_merged) <- final_data_merged$ions
# Remove ions column
final_data_merged$ions <- NULL
```


# Creating Dataframe for Data Without Batch Correction

```{r}
# Below we create a vector to specify the groups 
treatment_groups <- c("wt", "wt", "wt", "wt", "wt", "wt", "wt", "wt", 'wt', "tg", "tg", "tg", "tg", "tg", "tg", "tg", "tg", "tg")

# Create a vector to represent decjan and august batches
batch_groups <- c("decjan", "august", "august", "august", "august", "decjan", "august", "decjan", "decjan", "august", "decjan", "august", "decjan", "august", "august", "decjan", "decjan", "decjan")

# Create dataframe of both columns describing data 
data_for_coldata <- data.frame(treatment_groups, batch_groups)

# Make into a matrix
final_data_merged_matrix <- as.matrix(final_data_merged)
```

Below we run the pipeline without batch correction to see what the PCA looks like.

```{r}
# Make data into percentagemarized experiment object
raw_SE <- SummarizedExperiment(assays=list(counts=final_data_merged_matrix), colData = data_for_coldata)
# Put data through Maplet Pipeline
processed_SE <- raw_SE %>%
  mt_pre_trans_scale() %>% # Scale data (z-scores)
  mt_pre_outlier_to_na() %>% # Detect outliers (any values that lie outside the 0.025 and 0.975 regions when assuming a normal distribution)  and set to NA
  mt_pre_impute_knn() %>% # Impute missing values with knn imputation
  mt_pre_filter_missingness(feat_max = 0.5) # Remove ions with all missing values due to dividing by 0 in KNN

processed_SE <- processed_SE %>% 
  mt_plots_pca(color = processed_SE$treatment_groups) %>% #Create PCA plot colored by treatment
  mt_plots_pca(color = processed_SE$batch_groups) #Create PCA plot colored by batch
```

Plot the PCA below colored by treatment and batch.

```{r}
processed_SE@metadata$results$`plots_pca.680a325a-6b0e-40f6-bf77-0065ad09f97f`

processed_SE@metadata$results$`plots_pca.77c64f0c-fb92-4f4a-92b2-44b5762af677`
```

# Combat Batch Correction

1. create a SE for batch1 D1 ----
2. preprocess and impute D1 ----
3. create a SE D2 for batch2 -----
4. preprocess and impute D2 ----
5. merge preprocessed D1 and D2 and create a SE D ----
6. apply combat batch correction ----

```{r}
# Split into decjan and august batch data
august_data <- final_data_merged_matrix[, which(batch_groups == "august")]
decjan_data <- final_data_merged_matrix[, which(batch_groups == "decjan")]

# Create vector that represent "august" for august data and "decjan" for decjan data
batch_groups_august <- c(rep("august", ncol(august_data)))
batch_groups_decjan <- c(rep("decjan", ncol(decjan_data)))

# Create vector that represent treatments for august data
treatment_august <- treatment_groups[which(batch_groups == "august")]
# Create vector that represent CRE and CSE for decjan data
treatment_decjan <- treatment_groups[which(batch_groups == "decjan")]

# Create dataframe of both columns describing august data 
data_for_coldata_august <- data.frame(batch_groups_august, treatment_august)
# Create dataframe of both columns describing decjan data 
data_for_coldata_decjan <- data.frame(batch_groups_decjan, treatment_decjan)

# Make data into summarized experiment object
raw_SE_batch1 <- SummarizedExperiment(assays=list(counts=august_data), colData = data_for_coldata_august)
# Put data through Maplet Pipeline
processed_SE_batch1 <- raw_SE_batch1 %>%
  mt_pre_outlier_to_na() %>% # Detect outliers (any values that lie outside the 0.025 and 0.975 regions when assuming a normal distribution)  and set to NA
  mt_pre_impute_knn() %>% # Impute missing values with knn imputation
  mt_pre_filter_missingness(feat_max = 0.5) # Remove ions with all missing values due to dividing by 0 in KNN

# Make data into summarized experiment object
raw_SE_batch2 <- SummarizedExperiment(assays=list(counts=decjan_data), colData = data_for_coldata_decjan)
processed_SE_batch2 <- raw_SE_batch2 %>%
  mt_pre_outlier_to_na() %>% # Detect outliers (any values that lie outside the 0.025 and 0.975 regions when assuming a normal distribution)  and set to NA
  mt_pre_impute_knn() %>% # Impute missing values with knn imputation
  mt_pre_filter_missingness(feat_max = 0.5) # Remove ions with all missing values due to dividing by 0 in KNN

# Create dataframes of expression batch 1
batch1_data <- processed_SE_batch1@assays@data$counts
# Create dataframes of expression batch 2
batch2_data <- processed_SE_batch2@assays@data$counts
 
# Keep only m/z values in common between batches
final_data_for_maplet <- merge(batch1_data, batch2_data, by = 'row.names')

# Make m/z values rownames
rownames(final_data_for_maplet) <- final_data_for_maplet$Row.names
# Remove m/z column
final_data_for_maplet$Row.names <- NULL

# Create vector that represent "august" for august data and "decjan" for decjan data
batch_groups_final <- c(processed_SE_batch1$batch_groups_august, processed_SE_batch2$batch_groups_decjan)

# Create vector that represent treatment for final data
treatment_final <- c(treatment_august, treatment_decjan)

# Create dataframe of both columns describing final data 
data_for_coldata_final <- data.frame(batch_groups_final, treatment_final)

# Change column names to make them shorter
#colnames(final_data_for_maplet) <- c("210_a1tg_wtY", "270_5_Tg_wtY", "252_8_wt_wtY", "225_3tg_wtB", "226_a2_wt_wtB", "249_4_Tg_TgY", "226_a1_Tg_TgY", "268_a3_wt_TgY", "191_a3wt_TgB", "270_a1_Tg_TgB", "271_a3_Tg_wtY", "208_5wt_wtY", "225_a1wt_wtB", "225_4wt_wtB", "256_a3_Tg_TgY", "209_2wt_TgY", "268_3_Tg_TgB", "278_a2_wt_TgB")

# Create single summarized experiment object
SE_batches_final <- SummarizedExperiment(assays=list(counts= as.matrix(final_data_for_maplet)), colData = data_for_coldata_final, rowData = data.frame(name=rownames(final_data_for_maplet)))

SE_batches_final_combat <- SE_batches_final %>% 
  mt_clean_validate_se() %>%
  mt_load_flag_logged() %>%
  mt_pre_batch_combat(batch_col = "batch_groups_final") %>%
  mt_pre_trans_scale() %>%
  mt_pre_filter_missingness(feat_max = 0.5) # Remove ions with all missing values due to dividing by 0 in KNN

SE_batches_final_combat <- SE_batches_final_combat %>% 
  mt_plots_pca(color = SE_batches_final_combat$batch_groups_final) %>% # Create PCA plot after batch correction colored by batch
  mt_plots_pca(color = SE_batches_final_combat$treatment_final) %>% #Create PCA plot after batch correction colored by resistance type
mt_plots_pca(color = SE_batches_final_combat$treatment_final, shape=batch_groups_final) # Create pca plot after batch correction colored by resistance type and shaped by batch

# Make vector for batches
batch_data <- SE_batches_final_combat$batch_groups_final

final_assay <- assay(SE_batches_final_combat)

```

Below we create an object for the transposed data matrix after batch correction.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite <- t(final_assay)
```

Below we visualize all the PCA plots.

```{r}
SE_batches_final_combat@metadata$results$`plots_pca.25450f88-7637-46dc-8466-7874a25d09d8`

SE_batches_final_combat@metadata$results$`plots_pca.5ba08255-a0e0-428a-9bc2-2bbfdbe24a35`

SE_batches_final_combat@metadata$results$`plots_pca.d10e5fb5-d969-4c67-96eb-4c59f684d4f6`
```

Below we run an ANOVA to test if the distributions of metabolites are different between batches after batch correction. 

```{r}
# Make list for pvalues to be added to
aov_pval_list <- list()

final_statistics <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite[,i], batch_data)
    aov_test <- aov(metabolite ~ batch_groups_final, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list[[length(aov_pval_list) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_batch <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite), unlist(final_statistics))

significant_aov_dataframe_batch <- final_aov_dataframe_batch[final_aov_dataframe_batch$unlist.final_statistics. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_batch <- final_aov_dataframe_batch %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_batch$unlist.final_statistics., method = 'fdr'))

significant_aov_dataframe_with_correction_batch <- final_aov_dataframe_with_correction_batch[final_aov_dataframe_with_correction_batch$group_padj < 0.05, ]
```

Below we run an ANOVA to test if the distributions of metabolites are different. There are no significantly different metabolites between wt and Tg samples.

```{r}
# Make list for pvalues to be added to
aov_pval_list <- list()
treatment_final_wt_vs_tg <- ifelse(treatment_final %like% "w", "wt", "tg")

final_statistics <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite[,i], treatment_final_wt_vs_tg)
    aov_test <- aov(metabolite ~ treatment_final_wt_vs_tg, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list[[length(aov_pval_list) + 1]] <- aov_pval
}) 
  
# Create dataframe of metabolites and their anova pvalues
final_aov_dataframe <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite), unlist(final_statistics))

# Create dataframe of unadjusted significant pvalues 
significant_aov_dataframe <- final_aov_dataframe[final_aov_dataframe$unlist.final_statistics. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction <- final_aov_dataframe %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe$unlist.final_statistics., method = 'fdr'))

# Create dataframe of adjusted significant pvalues 
significant_aov_dataframe_with_correction <- final_aov_dataframe_with_correction[final_aov_dataframe_with_correction$group_padj < 0.05, ]
```


# Repeat with Median Batch Correction

Below we run median batch correction - dividing each batch by its median for each ion and then combining the results.

```{r}
august_data <- final_data_merged_matrix[, which(batch_groups == "august")]
median_august <- apply(august_data, 1, median, na.rm=TRUE)
august_data_final <- august_data/median_august
#Remove rows with NA's using na.omit()
august_data_final <- na.omit(august_data_final)

decjan_data <- final_data_merged_matrix[, which(batch_groups == "decjan")]
median_decjan <- apply(decjan_data, 1, median, na.rm=TRUE)
decjan_data_final <- decjan_data/median_decjan
#Remove rows with NA's using na.omit()
decjan_data_final <- na.omit(decjan_data_final)

# Keep only m/z values in common between batches
final_data_for_maplet <- merge(august_data_final, decjan_data_final, by = 'row.names')

# Make m/z values rownames
rownames(final_data_for_maplet) <- final_data_for_maplet$Row.names
# Remove m/z column
final_data_for_maplet$Row.names <- NULL

# Create single summarized experiment object
SE_batches_final <- SummarizedExperiment(assays=list(counts= as.matrix(final_data_for_maplet)), colData = data_for_coldata_final, rowData = data.frame(name=rownames(final_data_for_maplet)))

SE_batches_final_median <- SE_batches_final %>% 
  mt_pre_trans_scale()

SE_batches_final_median <- SE_batches_final_median %>% 
  mt_plots_pca(color = SE_batches_final_median$batch_groups_final) %>% # Create PCA plot after batch correction colored by batch
  mt_plots_pca(color = SE_batches_final_median$treatment_final) %>% #Create PCA plot after batch correction colored by resistance type
mt_plots_pca(color = SE_batches_final_median$treatment_final, shape=batch_groups_final) # Create pca plot after batch correction colored by resistance type and shaped by batch

# Make vector for batches
batch_data <- SE_batches_final_median$batch_groups_final

final_assay <- assay(SE_batches_final_median)
```

Below we visualize all the PCA plots.

```{r}
SE_batches_final_median@metadata$results$`plots_pca.c6387812-605f-4659-9379-ee65937ead03`

SE_batches_final_median@metadata$results$`plots_pca.8758a741-37c5-43e7-971a-f7424ee31cb7`

SE_batches_final_median@metadata$results$`plots_pca.4f2426e7-ac58-47a0-8d58-18addb5e5a0e`
```


# Everything with filtered ions

Below we import our filtered ions.

```{r}
filtered_ion_list <- read.csv('D:/NEW All AGE Negative masks and roi sums/Whole Brains/two_sd_filtered_ions_no_noise.csv', row.names = 1)

final_data_merged_matrix_filtered <- final_data_merged_matrix[rownames(final_data_merged_matrix) %in% filtered_ion_list$X0, ]
final_data_merged_matrix_filtered <- final_data_merged_matrix_filtered[!(row.names(final_data_merged_matrix_filtered) %in% c("299.9460")),]
```

Below we run the pipeline without batch correction to see what the PCA looks like.

```{r}
# Make data into summarized experiment object
raw_SE <- SummarizedExperiment(assays=list(counts=final_data_merged_matrix_filtered), colData = data_for_coldata)
# Put data through Maplet Pipeline
processed_SE <- raw_SE %>%
  mt_pre_trans_scale() %>% # Scale data (z-scores)
  mt_pre_outlier_to_na() %>% # Detect outliers (any values that lie outside the 0.025 and 0.975 regions when assuming a normal distribution)  and set to NA
  mt_pre_impute_knn() # Impute missing values with knn imputation


processed_SE <- processed_SE %>% 
  mt_plots_pca(color = processed_SE$treatment_groups) %>% #Create PCA plot colored by treatment
  mt_plots_pca(color = processed_SE$batch_groups) #Create PCA plot colored by batch
```

Plot the PCA below colored by treatment and batch.

```{r}
processed_SE@metadata$results$`plots_pca.5f54d0c7-9fd7-4e4e-9aee-ff223003422a`

processed_SE@metadata$results$`plots_pca.f3a08571-22be-48d3-b9dc-aeca5b73f929`
```

Below we run combat batch correction.

```{r}
august_data <- final_data_merged_matrix[, which(batch_groups == "august")]
august_data_filtered <- august_data[rownames(august_data) %in% filtered_ion_list$X0, ]
decjan_data <- final_data_merged_matrix[, which(batch_groups == "decjan")]
decjan_data_filtered <- decjan_data[rownames(decjan_data) %in% filtered_ion_list$X0, ]

# Make data into summarized experiment object
raw_SE_batch1 <- SummarizedExperiment(assays=list(counts=august_data_filtered), colData = data_for_coldata_august)
# Put data through Maplet Pipeline
processed_SE_batch1 <- raw_SE_batch1 %>%
  mt_pre_outlier_to_na() %>% # Detect outliers (any values that lie outside the 0.025 and 0.975 regions when assuming a normal distribution)  and set to NA
  mt_pre_impute_knn() # Impute missing values with knn imputation


# Make data into summarized experiment object
raw_SE_batch2 <- SummarizedExperiment(assays=list(counts=decjan_data_filtered), colData = data_for_coldata_decjan)
processed_SE_batch2 <- raw_SE_batch2 %>%
  mt_pre_outlier_to_na() %>% # Detect outliers (any values that lie outside the 0.025 and 0.975 regions when assuming a normal distribution)  and set to NA
  mt_pre_impute_knn() # Impute missing values with knn imputation

# Create dataframes of expression batch 1
batch1_data <- processed_SE_batch1@assays@data$counts
# Create dataframes of expression batch 2
batch2_data <- processed_SE_batch2@assays@data$counts
 
# Keep only m/z values in common between batches
final_data_for_maplet <- merge(batch1_data, batch2_data, by = 'row.names')

# Make m/z values rownames
rownames(final_data_for_maplet) <- final_data_for_maplet$Row.names
# Remove m/z column
final_data_for_maplet$Row.names <- NULL

# Create vector that represent "august" for august data and "decjan" for decjan data
batch_groups_final <- c(processed_SE_batch1$batch_groups_august, processed_SE_batch2$batch_groups_decjan)

# Create vector that represent treatment for final data
treatment_final <- c(treatment_august, treatment_decjan)

# Create dataframe of both columns describing final data 
data_for_coldata_final <- data.frame(batch_groups_final, treatment_final)

# Change column names to make them shorter
#colnames(final_data_for_maplet) <- c("210_a1tg_wtY", "270_5_Tg_wtY", "252_8_wt_wtY", "225_3tg_wtB", "226_a2_wt_wtB", "249_4_Tg_TgY", "226_a1_Tg_TgY", "268_a3_wt_TgY", "191_a3wt_TgB", "270_a1_Tg_TgB", "271_a3_Tg_wtY", "208_5wt_wtY", "225_a1wt_wtB", "225_4wt_wtB", "256_a3_Tg_TgY", "209_2wt_TgY", "268_3_Tg_TgB", "278_a2_wt_TgB")

# Create single summarized experiment object
SE_batches_final <- SummarizedExperiment(assays=list(counts= as.matrix(final_data_for_maplet)), colData = data_for_coldata_final, rowData = data.frame(name=rownames(final_data_for_maplet)))

SE_batches_not_standardized_combat <- SE_batches_final %>% 
  mt_clean_validate_se() %>%
  mt_load_flag_logged() %>%
  mt_pre_batch_combat(batch_col = "batch_groups_final") 
assay_not_standardized <- assay(SE_batches_not_standardized_combat)
write.csv(assay_not_standardized, "D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/AGE_negative_hippocampus_combat_batch_corrected_percentages.csv")

SE_batches_final_combat <- SE_batches_final %>% 
  mt_clean_validate_se() %>%
  mt_load_flag_logged() %>%
  mt_pre_batch_combat(batch_col = "batch_groups_final") %>%
  mt_pre_trans_scale()


SE_batches_final_combat <- SE_batches_final_combat %>% 
  mt_plots_pca(color = SE_batches_final_combat$batch_groups_final) %>% # Create PCA plot after batch correction colored by batch
  mt_plots_pca(color = SE_batches_final_combat$treatment_final) %>% #Create PCA plot after batch correction colored by resistance type
mt_plots_pca(color = SE_batches_final_combat$treatment_final, shape=batch_groups_final) # Create pca plot after batch correction colored by resistance type and shaped by batch

# Make vector for batches
batch_data <- SE_batches_final_combat$batch_groups_final

final_assay <- assay(SE_batches_final_combat)
```

Below we create an object for the transposed data matrix after batch correction.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite <- t(final_assay)
```

Below we visualize all the PCA plots.

```{r}
SE_batches_final_combat@metadata$results$`plots_pca.626516c1-c23e-474b-bb90-5b52fb70a330`

SE_batches_final_combat@metadata$results$`plots_pca.f369776a-90d0-4fcd-9a5a-d8d17cc9def8`

SE_batches_final_combat@metadata$results$`plots_pca.1a9359a5-8798-4cbf-a03c-b25a1fce7a10`
```

Below we run an ANOVA to test if the distributions of metabolites are different between batches after batch correction. 

```{r}
# Make list for pvalues to be added to
aov_pval_list <- list()

final_statistics <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite[,i], batch_data)
    aov_test <- aov(metabolite ~ batch_groups_final, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list[[length(aov_pval_list) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_batch <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite), unlist(final_statistics))

significant_aov_dataframe_batch <- final_aov_dataframe_batch[final_aov_dataframe_batch$unlist.final_statistics. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_batch <- final_aov_dataframe_batch %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_batch$unlist.final_statistics., method = 'fdr'))

significant_aov_dataframe_with_correction_batch <- final_aov_dataframe_with_correction_batch[final_aov_dataframe_with_correction_batch$group_padj < 0.05, ]
```

Below we run an ANOVA to test if the distributions of metabolites are different. There are no significantly different metabolites between wt and Tg samples.

```{r}
# Make list for pvalues to be added to
aov_pval_list <- list()
treatment_final_wt_vs_tg <- ifelse(treatment_final %like% "w", "wt", "tg")

final_statistics <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite[,i], treatment_final_wt_vs_tg)
    aov_test <- aov(metabolite ~ treatment_final_wt_vs_tg, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list[[length(aov_pval_list) + 1]] <- aov_pval
}) 
  
# Create dataframe of metabolites and their anova pvalues
final_aov_dataframe <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite), unlist(final_statistics))

# Create dataframe of unadjusted significant pvalues 
significant_aov_dataframe <- final_aov_dataframe[final_aov_dataframe$unlist.final_statistics. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction <- final_aov_dataframe %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe$unlist.final_statistics., method = 'fdr'))

# Create dataframe of adjusted significant pvalues 
significant_aov_dataframe_with_correction <- final_aov_dataframe_with_correction[final_aov_dataframe_with_correction$group_padj < 0.05, ]
```

# Repeat with Median Batch Correction

Below we run median batch correction - dividing each batch by its median for each ion and then combining the results.

```{r}
august_data <- final_data_merged_matrix_filtered[, which(batch_groups == "august")]
median_august <- apply(august_data, 1, median, na.rm=TRUE)
august_data_final <- august_data/median_august

decjan_data <- final_data_merged_matrix_filtered[, which(batch_groups == "decjan")]
median_decjan <- apply(decjan_data, 1, median, na.rm=TRUE)
decjan_data_final <- decjan_data/median_decjan
 
# Keep only m/z values in common between batches
final_data_for_maplet <- merge(august_data_final, decjan_data_final, by = 'row.names')

# Make m/z values rownames
rownames(final_data_for_maplet) <- final_data_for_maplet$Row.names
# Remove m/z column
final_data_for_maplet$Row.names <- NULL

# Create single summarized experiment object
SE_batches_final <- SummarizedExperiment(assays=list(counts= as.matrix(final_data_for_maplet)), colData = data_for_coldata_final, rowData = data.frame(name=rownames(final_data_for_maplet)))

# Save median batch correction matrix
median_batch_corrected_data_ions_of_interest <- assay(SE_batches_final)
#write.csv(median_batch_corrected_data_ions_of_interest, file = "D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/AGE_median_batch_corrected_sums_ions_of_interest.csv")

SE_batches_final_median <- SE_batches_final %>% 
  mt_pre_trans_scale()

SE_batches_final_median <- SE_batches_final_median %>% 
  mt_plots_pca(color = SE_batches_final_median$batch_groups_final) %>% # Create PCA plot after batch correction colored by batch
  mt_plots_pca(color = SE_batches_final_median$treatment_final) %>% #Create PCA plot after batch correction colored by resistance type
mt_plots_pca(color = SE_batches_final_median$treatment_final, shape=batch_groups_final) # Create pca plot after batch correction colored by resistance type and shaped by batch

# Make vector for batches
batch_data <- SE_batches_final_median$batch_groups_final

final_assay <- assay(SE_batches_final_median)
```

Below we visualize all the PCA plots.

```{r}
SE_batches_final_median@metadata$results$`plots_pca.e5081316-7f93-4fd7-9ea1-15e289aa51aa`

SE_batches_final_median@metadata$results$`plots_pca.1f6cb7d5-c01e-4979-ae59-cb4d89755d13`

SE_batches_final_median@metadata$results$`plots_pca.fd9d94fa-fb2c-4455-87bc-0ef50d3693c7`
```

Below we create an object for the transposed data matrix after batch correction.

```{r}
processed_metabolite_values_median_final_sample_by_metabolite <- t(final_assay)
```

Below we run an ANOVA to test if the distributions of metabolites are different between batches after batch correction. 

```{r}
# Make list for pvalues to be added to
aov_pval_list <- list()

final_statistics <- lapply(1:ncol(processed_metabolite_values_median_final_sample_by_metabolite), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_median_final_sample_by_metabolite[,i], batch_data)
    aov_test <- aov(metabolite ~ batch_groups_final, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list[[length(aov_pval_list) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_batch <- data.frame(colnames(processed_metabolite_values_median_final_sample_by_metabolite), unlist(final_statistics))

significant_aov_dataframe_batch <- final_aov_dataframe_batch[final_aov_dataframe_batch$unlist.final_statistics. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_batch <- final_aov_dataframe_batch %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_batch$unlist.final_statistics., method = 'fdr'))

significant_aov_dataframe_with_correction_batch <- final_aov_dataframe_with_correction_batch[final_aov_dataframe_with_correction_batch$group_padj < 0.05, ]
```

Below we run an ANOVA to test if the distributions of metabolites are different. There are no significantly different metabolites between wt and Tg samples.

```{r}
# Make list for pvalues to be added to
aov_pval_list <- list()
treatment_final_wt_vs_tg <- ifelse(treatment_final %like% "w", "wt", "tg")

final_statistics <- lapply(1:ncol(processed_metabolite_values_median_final_sample_by_metabolite), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_median_final_sample_by_metabolite[,i], treatment_final_wt_vs_tg)
    aov_test <- aov(metabolite ~ treatment_final_wt_vs_tg, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list[[length(aov_pval_list) + 1]] <- aov_pval
}) 
  
# Create dataframe of metabolites and their anova pvalues
final_aov_dataframe <- data.frame(colnames(processed_metabolite_values_median_final_sample_by_metabolite), unlist(final_statistics))

# Create dataframe of unadjusted significant pvalues 
significant_aov_dataframe <- final_aov_dataframe[final_aov_dataframe$unlist.final_statistics. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction <- final_aov_dataframe %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe$unlist.final_statistics., method = 'fdr'))

# Create dataframe of adjusted significant pvalues 
significant_aov_dataframe_with_correction <- final_aov_dataframe_with_correction[final_aov_dataframe_with_correction$group_padj < 0.05, ]
```

# Statistical testing between specific phenotypes


Below we run ANOVA to see if there are differences between all groups.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_anova_all <- processed_metabolite_values_combat_final_sample_by_metabolite
# Create identification list for just tg light samples
treatment_final_all <- c("wt_6mo", "wt_6mo", "wt_12mo", "wt_12mo", "wt_22mo", "tg_6mo", "tg_6mo", "tg_6mo", "tg_12mo", "wt_6mo", "wt_12mo", "wt_22mo", "wt_22mo", "tg_12mo", "tg_12mo", "tg_22mo", "tg_22mo", "tg_22mo")

# Make list for pvalues to be added to
aov_pval_list_all <- list()

final_statistics_anova_all <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_anova_all), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_anova_all[,i], treatment_final_all)
    aov_test <- aov(metabolite ~ treatment_final_all, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_all[[length(aov_pval_list_all) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_all <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_anova_all), unlist(final_statistics_anova_all))

significant_aov_dataframe_anova_all <- final_aov_dataframe_anova_all[final_aov_dataframe_anova_all$unlist.final_statistics_anova_all. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_all <- final_aov_dataframe_anova_all %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_all$unlist.final_statistics_anova_all., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_all <- final_aov_dataframe_with_correction_anova_all[final_aov_dataframe_with_correction_anova_all$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo, 12mo, and 22mo for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/6mo_vs_12mo_vs_22mo_significant_all_ANOVA_ion_",ion,".png"))
boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_anova_all[, ion] ~ factor(treatment_final_all, levels = c('wt_6mo', 'wt_12mo', 'wt_22mo', 'tg_6mo', 'tg_12mo', 'tg_22mo')), las = 2, main=paste("Ion distribution all groups", ion), xlab = "", ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we perform statistical testing for the 6mo mice with only the significant ions from the ANOVA with all groups.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_6mo <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_a1wt|225_4wt|226_a2_wt|225_3tg|225_a2tg|226_a1tg",]
# Create subset of identification list for just 6mo light samples
treatment_final_6mo <- c("wt", "wt", "tg", "tg", "tg", "wt")
# Create subset for just 6mo light samples
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_6mo[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]
# Create subset of identification list for just 6mo light samples
ttest_pval_list_6mo_after_anova <- list()
final_statistics_6mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova), function(i){
    ttest_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova[,i], treatment_final_6mo)
    t_test <- t.test(metabolite ~ treatment_final_6mo, data = ttest_df, var.equal = TRUE)
    ttest_pval <- t_test$p.value
    ttest_pval_list_6mo_after_anova[[length(ttest_pval_list_6mo_after_anova) + 1]] <- ttest_pval
})
final_ttest_dataframe_6mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova), unlist(final_statistics_6mo_after_anova))
significant_ttest_dataframe_6mo_after_anova <- final_ttest_dataframe_6mo_after_anova[final_ttest_dataframe_6mo_after_anova$unlist.final_statistics_6mo_after_anova. < 0.05, ]
# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_ttest_dataframe_with_correction_6mo_after_anova <- final_ttest_dataframe_6mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_ttest_dataframe_6mo_after_anova$unlist.final_statistics_6mo_after_anova., method = 'fdr'))
significant_ttest_dataframe_with_correction_6mo_after_anova <- final_ttest_dataframe_with_correction_6mo_after_anova[final_ttest_dataframe_with_correction_6mo_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for wt and Tg for the significant ions without FDR correction.

```{r}
for (ion in significant_ttest_dataframe_6mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/wt_vs_tg_significant_6mo_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo[, ion] ~ treatment_final_6mo, main="Ion distribution WT vs Tg 6mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

# Repeat for significant with correction
for (ion in significant_ttest_dataframe_with_correction_6mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/wt_vs_tg_significant_with_correction_6mo_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo[, ion] ~ treatment_final_6mo, main="Ion distribution WT vs Tg 6mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we perform statistical testing for the 12mo mice with only the significant ions from the ANOVA with all groups.

```{r}
# Create subset for just 12mo light samples
processed_metabolite_values_combat_final_sample_by_metabolite_12mo <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "208_5wt|209_2wt|278_a2_wt|210_a1tg|270_a1_Tg|270_5_Tg",]
# Create subset of identification list for just 12mo light samples
treatment_final_12mo <- c("wt", "wt", "tg", "wt", "tg", "tg")
processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_12mo[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]
# Create subset of identification list for just 12mo light samples
ttest_pval_list_12mo_after_anova <- list()
final_statistics_12mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova), function(i){
    ttest_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova[,i], treatment_final_12mo)
    t_test <- t.test(metabolite ~ treatment_final_12mo, data = ttest_df, var.equal = TRUE)
    ttest_pval <- t_test$p.value
    ttest_pval_list_12mo_after_anova[[length(ttest_pval_list_12mo_after_anova) + 1]] <- ttest_pval
})
final_ttest_dataframe_12mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova), unlist(final_statistics_12mo_after_anova))
significant_ttest_dataframe_12mo_after_anova <- final_ttest_dataframe_12mo_after_anova[final_ttest_dataframe_12mo_after_anova$unlist.final_statistics_12mo_after_anova. < 0.05, ]
# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_ttest_dataframe_with_correction_12mo_after_anova <- final_ttest_dataframe_12mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_ttest_dataframe_12mo_after_anova$unlist.final_statistics_12mo_after_anova., method = 'fdr'))
significant_ttest_dataframe_with_correction_12mo_after_anova <- final_ttest_dataframe_with_correction_12mo_after_anova[final_ttest_dataframe_with_correction_12mo_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for wt and Tg for the significant ions without FDR correction.

```{r}
for (ion in significant_ttest_dataframe_12mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/wt_vs_tg_significant_12mo_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_12mo[, ion] ~ treatment_final_12mo, main="Ion distribution WT vs Tg 12mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

# Repeat for significant with correction
for (ion in significant_ttest_dataframe_with_correction_12mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/wt_vs_tg_significant_with_correction_12mo_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_12mo[, ion] ~ treatment_final_12mo, main="Ion distribution WT vs Tg 12mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we perform statistical testing for the 22mo mice with only the significant ions from the ANOVA with all groups.

```{r}
# Create subset for just 22mo samples
processed_metabolite_values_combat_final_sample_by_metabolite_22mo <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "191_a3wt|252_8_wt|268_a3_wt|249_4_Tg|256_a3_Tg|268_3_Tg",]
# Create subset of identification list for just 22mo light samples
treatment_final_22mo <- c("wt", "wt", "wt", "tg", "tg", "tg")
processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_22mo[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]
# Create subset of identification list for just 22mo light samples
ttest_pval_list_22mo_after_anova <- list()
final_statistics_22mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova), function(i){
    ttest_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova[,i], treatment_final_22mo)
    t_test <- t.test(metabolite ~ treatment_final_22mo, data = ttest_df, var.equal = TRUE)
    ttest_pval <- t_test$p.value
    ttest_pval_list_22mo_after_anova[[length(ttest_pval_list_22mo_after_anova) + 1]] <- ttest_pval
})
final_ttest_dataframe_22mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova), unlist(final_statistics_22mo_after_anova))
significant_ttest_dataframe_22mo_after_anova <- final_ttest_dataframe_22mo_after_anova[final_ttest_dataframe_22mo_after_anova$unlist.final_statistics_22mo_after_anova. < 0.05, ]
# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_ttest_dataframe_with_correction_22mo_after_anova <- final_ttest_dataframe_22mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_ttest_dataframe_22mo_after_anova$unlist.final_statistics_22mo_after_anova., method = 'fdr'))
significant_ttest_dataframe_with_correction_22mo_after_anova <- final_ttest_dataframe_with_correction_22mo_after_anova[final_ttest_dataframe_with_correction_22mo_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for wt and Tg for the significant ions without FDR correction.

```{r}
for (ion in significant_ttest_dataframe_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/wt_vs_tg_significant_22mo_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_22mo[, ion] ~ treatment_final_22mo, main="Ion distribution WT vs Tg 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

# Repeat for significant with correction
for (ion in significant_ttest_dataframe_with_correction_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/wt_vs_tg_significant_with_correction_22mo_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_22mo[, ion] ~ treatment_final_22mo, main="Ion distribution WT vs Tg 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we run ANOVA to see if there are differences between wt over time.

```{r}
# Create subset for just wt light samples
processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_a1wt|225_4wt|226_a2_wt|208_5wt|209_2wt|278_a2_wt|191_a3wt|252_8_wt|268_a3_wt",]
# Create subset of identification list for just wt light samples
treatment_final_wt <- c("6mo", "6mo", "12mo", "12mo", "22mo", "6mo", "12mo", "22mo", "22mo")
# Create subset for just 12mo light samples
processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_wt_after_anova <- list()

final_statistics_anova_wt_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova[,i], treatment_final_wt)
    aov_test <- aov(metabolite ~ treatment_final_wt, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_wt_after_anova[[length(aov_pval_list_wt_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_wt_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova), unlist(final_statistics_anova_wt_after_anova))

significant_aov_dataframe_anova_wt_after_anova <- final_aov_dataframe_anova_wt_after_anova[final_aov_dataframe_anova_wt_after_anova$unlist.final_statistics_anova_wt_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_wt_after_anova <- final_aov_dataframe_anova_wt_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_wt_after_anova$unlist.final_statistics_anova_wt_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_wt_after_anova <- final_aov_dataframe_with_correction_anova_wt_after_anova[final_aov_dataframe_with_correction_anova_wt_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo, 12mo, and 22mo for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_wt_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/6mo_vs_12mo_vs_22mo_significant_wt_ANOVA_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt[, ion] ~ factor(treatment_final_wt, levels = c('6mo', '12mo', '22mo')), main="Ion distribution WT 6mo vs 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

# Repeat for significant with correction
for (ion in significant_aov_dataframe_with_correction_anova_wt_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/6mo_vs_12mo_vs_22mo_significant_with_correction_wt_ANOVA_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova[, ion] ~ factor(treatment_final_wt, levels = c('6mo', '12mo', '22mo')), main="Ion distribution WT 6mo vs 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we run ANOVA to see if there are differences between tg over time.

```{r}
# Create subset for just tg light samples
processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_3tg|225_a2tg|226_a1tg|210_a1tg|270_a1_Tg|270_5_Tg|249_4_Tg|256_a3_Tg|268_3_Tg",]
# Create subset of identification list for just tg light samples
treatment_final_tg <- c("6mo", "6mo", "6mo", "12mo", "12mo", "12mo", "22mo", "22mo", "22mo")
# Create subset for just 12mo light samples
processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_tg_after_anova <- list()

final_statistics_anova_tg_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova[,i], treatment_final_tg)
    aov_test <- aov(metabolite ~ treatment_final_tg, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_tg_after_anova[[length(aov_pval_list_tg_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_tg_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova), unlist(final_statistics_anova_tg_after_anova))

significant_aov_dataframe_anova_tg_after_anova <- final_aov_dataframe_anova_tg_after_anova[final_aov_dataframe_anova_tg_after_anova$unlist.final_statistics_anova_tg_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_tg_after_anova <- final_aov_dataframe_anova_tg_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_tg_after_anova$unlist.final_statistics_anova_tg_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_tg_after_anova <- final_aov_dataframe_with_correction_anova_tg_after_anova[final_aov_dataframe_with_correction_anova_tg_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo, 12mo, and 22mo for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_tg_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/6mo_vs_12mo_vs_22mo_significant_tg_ANOVA_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg[, ion] ~ factor(treatment_final_tg, levels = c('6mo', '12mo', '22mo')), main="Ion distribution tg 6mo vs 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

# Repeat for significant with correction
for (ion in significant_aov_dataframe_with_correction_anova_tg_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots/6mo_vs_12mo_vs_22mo_significant_with_correction_tg_ANOVA_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova[, ion] ~ factor(treatment_final_tg, levels = c('6mo', '12mo', '22mo')), main="Ion distribution tg 6mo vs 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we save the statistical results.

```{r}
colnames(final_aov_dataframe_with_correction_anova_all)[colnames(final_aov_dataframe_with_correction_anova_all) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_all)[colnames(final_aov_dataframe_with_correction_anova_all) == "unlist.final_statistics_anova_all."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_all)[colnames(final_aov_dataframe_with_correction_anova_all) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_all, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Normalized By Pixel/AGE_hippocampus_all_samples_ANOVA_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_ttest_dataframe_with_correction_6mo_after_anova)[colnames(final_ttest_dataframe_with_correction_6mo_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_after_anova."] = "ion"
colnames(final_ttest_dataframe_with_correction_6mo_after_anova)[colnames(final_ttest_dataframe_with_correction_6mo_after_anova) == "unlist.final_statistics_6mo_after_anova."] = "pval"
colnames(final_ttest_dataframe_with_correction_6mo_after_anova)[colnames(final_ttest_dataframe_with_correction_6mo_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_ttest_dataframe_with_correction_6mo_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Normalized By Pixel/AGE_6mo_hippocampus_wt_vs_tg_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_ttest_dataframe_with_correction_12mo_after_anova)[colnames(final_ttest_dataframe_with_correction_12mo_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_after_anova."] = "ion"
colnames(final_ttest_dataframe_with_correction_12mo_after_anova)[colnames(final_ttest_dataframe_with_correction_12mo_after_anova) == "unlist.final_statistics_12mo_after_anova."] = "pval"
colnames(final_ttest_dataframe_with_correction_12mo_after_anova)[colnames(final_ttest_dataframe_with_correction_12mo_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_ttest_dataframe_with_correction_12mo_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Normalized By Pixel/AGE_12mo_hippocampus_wt_vs_tg_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_ttest_dataframe_with_correction_22mo_after_anova)[colnames(final_ttest_dataframe_with_correction_22mo_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_22mo_after_anova."] = "ion"
colnames(final_ttest_dataframe_with_correction_22mo_after_anova)[colnames(final_ttest_dataframe_with_correction_22mo_after_anova) == "unlist.final_statistics_22mo_after_anova."] = "pval"
colnames(final_ttest_dataframe_with_correction_22mo_after_anova)[colnames(final_ttest_dataframe_with_correction_22mo_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_ttest_dataframe_with_correction_22mo_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Normalized By Pixel/AGE_22mo_hippocampus_wt_vs_tg_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_wt_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_wt_after_anova."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_wt_after_anova) == "unlist.final_statistics_anova_wt_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_wt_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_wt_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Normalized By Pixel/AGE_hippocampus_wt_ANOVA_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_tg_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_tg_after_anova."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_tg_after_anova) == "unlist.final_statistics_anova_tg_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_tg_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_tg_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Normalized By Pixel/AGE_hippocampus_tg_ANOVA_filtered_ions_statistical_results.csv', row.names=FALSE)
```


# Testing specific wild type and Tg

Below we statistically test the 6mo and 12mo WT.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_a1wt|225_4wt|226_a2_wt|208_5wt|209_2wt|278_a2_wt",]
treatment_final_wt_6mo_12mo <- c("6mo", "6mo", "12mo", "12mo", "6mo", "12mo")
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt <- processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt[,
significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_wt_6mo_12mo_after_anova <- list()

final_statistics_anova_wt_6mo_12mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt[,i], treatment_final_wt_6mo_12mo)
    aov_test <- aov(metabolite ~ treatment_final_wt_6mo_12mo, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_wt_6mo_12mo_after_anova[[length(aov_pval_list_wt_6mo_12mo_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_wt_6mo_12mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt), unlist(final_statistics_anova_wt_6mo_12mo_after_anova))

significant_aov_dataframe_anova_wt_6mo_12mo_after_anova <- final_aov_dataframe_anova_wt_6mo_12mo_after_anova[final_aov_dataframe_anova_wt_6mo_12mo_after_anova$unlist.final_statistics_anova_wt_6mo_12mo_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova <- final_aov_dataframe_anova_wt_6mo_12mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_wt_6mo_12mo_after_anova$unlist.final_statistics_anova_wt_6mo_12mo_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_wt_6mo_12mo_after_anova <- final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova[final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo and 12mo wt for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_wt_6mo_12mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_12mo_wt_only_significant_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt[, ion] ~ factor(treatment_final_wt_6mo_12mo, levels = c('6mo', '12mo')), main="Ion distribution wt 6mo vs 12mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

for (ion in significant_aov_dataframe_with_correction_anova_wt_6mo_12mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_12mo_wt_only_significant_with_correction_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt[, ion] ~ factor(treatment_final_wt_6mo_12mo, levels = c('6mo', '12mo')), main="Ion distribution wt 6mo vs 12mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we statistically test the 6mo and 22mo WT.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_a1wt|225_4wt|226_a2_wt|191_a3wt|252_8_wt|268_a3_wt",]
treatment_final_wt_6mo_22mo <- c("6mo", "6mo", "22mo", "6mo", "22mo", "22mo")
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt <- processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt[,
significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_wt_6mo_22mo_after_anova <- list()

final_statistics_anova_wt_6mo_22mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt[,i], treatment_final_wt_6mo_22mo)
    aov_test <- aov(metabolite ~ treatment_final_wt_6mo_22mo, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_wt_6mo_22mo_after_anova[[length(aov_pval_list_wt_6mo_22mo_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_wt_6mo_22mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt), unlist(final_statistics_anova_wt_6mo_22mo_after_anova))

significant_aov_dataframe_anova_wt_6mo_22mo_after_anova <- final_aov_dataframe_anova_wt_6mo_22mo_after_anova[final_aov_dataframe_anova_wt_6mo_22mo_after_anova$unlist.final_statistics_anova_wt_6mo_22mo_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova <- final_aov_dataframe_anova_wt_6mo_22mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_wt_6mo_22mo_after_anova$unlist.final_statistics_anova_wt_6mo_22mo_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_wt_6mo_22mo_after_anova <- final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova[final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo and 22mo wt for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_wt_6mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_22mo_wt_only_significant_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt[, ion] ~ factor(treatment_final_wt_6mo_22mo, levels = c('6mo', '22mo')), main="Ion distribution wt 6mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

for (ion in significant_aov_dataframe_with_correction_anova_wt_6mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_22mo_wt_only_significant_with_correction_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt[, ion] ~ factor(treatment_final_wt_6mo_22mo, levels = c('6mo', '22mo')), main="Ion distribution wt 6mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we statistically test the 12mo and 22mo WT.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "208_5wt|209_2wt|278_a2_wt|191_a3wt|252_8_wt|268_a3_wt",]
treatment_final_wt_12mo_22mo <- c("12mo", "12mo", "22mo", "22mo", "22mo", "12mo")
processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt <- processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt[,
significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_wt_12mo_22mo_after_anova <- list()

final_statistics_anova_wt_12mo_22mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt[,i], treatment_final_wt_12mo_22mo)
    aov_test <- aov(metabolite ~ treatment_final_wt_12mo_22mo, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_wt_12mo_22mo_after_anova[[length(aov_pval_list_wt_12mo_22mo_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_wt_12mo_22mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt), unlist(final_statistics_anova_wt_12mo_22mo_after_anova))

significant_aov_dataframe_anova_wt_12mo_22mo_after_anova <- final_aov_dataframe_anova_wt_12mo_22mo_after_anova[final_aov_dataframe_anova_wt_12mo_22mo_after_anova$unlist.final_statistics_anova_wt_12mo_22mo_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova <- final_aov_dataframe_anova_wt_12mo_22mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_wt_12mo_22mo_after_anova$unlist.final_statistics_anova_wt_12mo_22mo_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_wt_12mo_22mo_after_anova <- final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova[final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 12mo and 22mo wt for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_wt_12mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/12mo_vs_22mo_wt_only_significant_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt[, ion] ~ factor(treatment_final_wt_12mo_22mo, levels = c('12mo', '22mo')), main="Ion distribution wt 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

for (ion in significant_aov_dataframe_with_correction_anova_wt_12mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/12mo_vs_22mo_wt_only_significant_with_correction_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt[, ion] ~ factor(treatment_final_wt_12mo_22mo, levels = c('12mo', '22mo')), main="Ion distribution wt 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we statistically test the 6mo and 12mo tg.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_3tg|225_a2tg|226_a1tg|210_a1tg|270_a1_Tg|270_5_Tg",]
treatment_final_tg_6mo_12mo <- c("6mo", "6mo", "6mo", "12mo", "12mo", "12mo")
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg <- processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg[,
significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_tg_6mo_12mo_after_anova <- list()

final_statistics_anova_tg_6mo_12mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg[,i], treatment_final_tg_6mo_12mo)
    aov_test <- aov(metabolite ~ treatment_final_tg_6mo_12mo, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_tg_6mo_12mo_after_anova[[length(aov_pval_list_tg_6mo_12mo_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_tg_6mo_12mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg), unlist(final_statistics_anova_tg_6mo_12mo_after_anova))

significant_aov_dataframe_anova_tg_6mo_12mo_after_anova <- final_aov_dataframe_anova_tg_6mo_12mo_after_anova[final_aov_dataframe_anova_tg_6mo_12mo_after_anova$unlist.final_statistics_anova_tg_6mo_12mo_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova <- final_aov_dataframe_anova_tg_6mo_12mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_tg_6mo_12mo_after_anova$unlist.final_statistics_anova_tg_6mo_12mo_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_tg_6mo_12mo_after_anova <- final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova[final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo and 12mo tg for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_tg_6mo_12mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_12mo_tg_only_significant_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg[, ion] ~ factor(treatment_final_tg_6mo_12mo, levels = c('6mo', '12mo')), main="Ion distribution tg 6mo vs 12mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

for (ion in significant_aov_dataframe_with_correction_anova_tg_6mo_12mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_12mo_tg_only_significant_with_correction_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg[, ion] ~ factor(treatment_final_tg_6mo_12mo, levels = c('6mo', '12mo')), main="Ion distribution tg 6mo vs 12mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we statistically test the 6mo and 22mo tg.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "225_3tg|225_a2tg|226_a1tg|249_4_Tg|256_a3_Tg|268_3_Tg",]
treatment_final_tg_6mo_22mo <- c("6mo", "6mo", "6mo", "22mo", "22mo", "22mo")
processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg <- processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg[,
significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_tg_6mo_22mo_after_anova <- list()

final_statistics_anova_tg_6mo_22mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg[,i], treatment_final_tg_6mo_22mo)
    aov_test <- aov(metabolite ~ treatment_final_tg_6mo_22mo, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_tg_6mo_22mo_after_anova[[length(aov_pval_list_tg_6mo_22mo_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_tg_6mo_22mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg), unlist(final_statistics_anova_tg_6mo_22mo_after_anova))

significant_aov_dataframe_anova_tg_6mo_22mo_after_anova <- final_aov_dataframe_anova_tg_6mo_22mo_after_anova[final_aov_dataframe_anova_tg_6mo_22mo_after_anova$unlist.final_statistics_anova_tg_6mo_22mo_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova <- final_aov_dataframe_anova_tg_6mo_22mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_tg_6mo_22mo_after_anova$unlist.final_statistics_anova_tg_6mo_22mo_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_tg_6mo_22mo_after_anova <- final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova[final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 6mo and 22mo tg for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_tg_6mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_22mo_tg_only_significant_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg[, ion] ~ factor(treatment_final_tg_6mo_22mo, levels = c('6mo', '22mo')), main="Ion distribution tg 6mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

for (ion in significant_aov_dataframe_with_correction_anova_tg_6mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/6mo_vs_22mo_tg_only_significant_with_correction_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg[, ion] ~ factor(treatment_final_tg_6mo_22mo, levels = c('6mo', '22mo')), main="Ion distribution tg 6mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we statistically test the 12mo and 22mo tg.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg <- processed_metabolite_values_combat_final_sample_by_metabolite[rownames(processed_metabolite_values_combat_final_sample_by_metabolite) %like% "210_a1tg|270_a1_Tg|270_5_Tg|249_4_Tg|256_a3_Tg|268_3_Tg",]
treatment_final_tg_12mo_22mo <- c("12mo", "12mo", "12mo", "22mo", "22mo", "22mo")
processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg <- processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg[,
significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]

# Make list for pvalues to be added to
aov_pval_list_tg_12mo_22mo_after_anova <- list()

final_statistics_anova_tg_12mo_22mo_after_anova <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg[,i], treatment_final_tg_12mo_22mo)
    aov_test <- aov(metabolite ~ treatment_final_tg_12mo_22mo, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_tg_12mo_22mo_after_anova[[length(aov_pval_list_tg_12mo_22mo_after_anova) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_tg_12mo_22mo_after_anova <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg), unlist(final_statistics_anova_tg_12mo_22mo_after_anova))

significant_aov_dataframe_anova_tg_12mo_22mo_after_anova <- final_aov_dataframe_anova_tg_12mo_22mo_after_anova[final_aov_dataframe_anova_tg_12mo_22mo_after_anova$unlist.final_statistics_anova_tg_12mo_22mo_after_anova. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova <- final_aov_dataframe_anova_tg_12mo_22mo_after_anova %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_tg_12mo_22mo_after_anova$unlist.final_statistics_anova_tg_12mo_22mo_after_anova., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_tg_12mo_22mo_after_anova <- final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova[final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova$group_padj < 0.05, ]
```

Below we visualize the distribution of the metabolites for 12mo and 22mo tg for the significant ions without FDR correction.

```{r}
for (ion in significant_aov_dataframe_anova_tg_12mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/12mo_vs_22mo_tg_only_significant_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg[, ion] ~ factor(treatment_final_tg_12mo_22mo, levels = c('12mo', '22mo')), main="Ion distribution tg 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}

for (ion in significant_aov_dataframe_with_correction_anova_tg_12mo_22mo_after_anova$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg.){
png(filename=paste("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots Filtered By Anova Within Phenotype Testing/12mo_vs_22mo_tg_only_significant_with_correction_ttest_ion_",ion,".png"))
  boxplot(processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg[, ion] ~ factor(treatment_final_tg_12mo_22mo, levels = c('12mo', '22mo')), main="Ion distribution tg 12mo vs 22mo",
   xlab=paste("Ion m/z value", ion), ylab="Z-scored Percentage")
#  get(i) ## may have to print, too:. print(get(I))
  dev.off()
}
```

Below we save the statistical results.

```{r}
colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_wt."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova) == "unlist.final_statistics_anova_wt_6mo_12mo_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_6mo_12mo_wt_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Within Phenotype Testing/AGE_negative_hippocampus_6mo_vs_12mo_wt_only_ttest_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_wt."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova) == "unlist.final_statistics_anova_wt_6mo_22mo_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_6mo_22mo_wt_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Within Phenotype Testing/AGE_negative_hippocampus_6mo_vs_22mo_wt_only_ttest_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_wt."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova) == "unlist.final_statistics_anova_wt_12mo_22mo_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova)[colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_12mo_22mo_wt_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Within Phenotype Testing/AGE_negative_hippocampus_12mo_vs_22mo_wt_only_ttest_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_12mo_tg."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova) == "unlist.final_statistics_anova_tg_6mo_12mo_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_6mo_12mo_tg_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Within Phenotype Testing/AGE_negative_hippocampus_6mo_vs_12mo_tg_only_ttest_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_6mo_22mo_tg."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova) == "unlist.final_statistics_anova_tg_6mo_22mo_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_6mo_22mo_tg_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Within Phenotype Testing/AGE_negative_hippocampus_6mo_vs_22mo_tg_only_ttest_filtered_ions_statistical_results.csv', row.names=FALSE)

colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova) == "colnames.processed_metabolite_values_combat_final_sample_by_metabolite_12mo_22mo_tg."] = "ion"
colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova) == "unlist.final_statistics_anova_tg_12mo_22mo_after_anova."] = "pval"
colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova)[colnames(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova) == "group_padj"] = "fdr_adjusted_pval"
write.csv(final_aov_dataframe_with_correction_anova_12mo_22mo_tg_after_anova, 'D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Average Hippocampus Statistical Testing Results Within Phenotype Testing/AGE_negative_hippocampus_12mo_vs_22mo_tg_only_ttest_filtered_ions_statistical_results.csv', row.names=FALSE)
```


# Making Pretty Plots for Publication

Below we run combat batch correction without standardizing the data.

```{r}
# Create single summarized experiment object
SE_batches_final_not_standardized <- SummarizedExperiment(assays=list(counts= as.matrix(final_data_for_maplet)), colData = data_for_coldata_final, rowData = data.frame(name=rownames(final_data_for_maplet)))

SE_batches_final_not_standardized_combat <- SE_batches_final_not_standardized %>% 
  mt_clean_validate_se() %>%
  mt_load_flag_logged() %>%
  mt_pre_batch_combat(batch_col = "batch_groups_final")

# Make vector for batches
batch_data <- SE_batches_final_not_standardized_combat$batch_groups_final

final_assay <- assay(SE_batches_final_not_standardized_combat)
processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized <- t(final_assay)

```

Below we run ANOVA to see if there are differences between all groups.

```{r}
processed_metabolite_values_combat_final_sample_by_metabolite_anova_all_not_standardized <- processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]
# Create identification list for just tg light samples
treatment_final_all <- c("wt_6mo", "wt_12mo", "wt_12mo", "tg_6mo", "tg_12mo", "wt_22mo", "tg_6mo", "wt_6mo", "tg_22mo", "wt_22mo", "tg_22mo", "tg_22mo", "wt_22mo", "tg_12mo", "tg_12mo", "wt_12mo", "tg_6mo", "wt_6mo")

# Make list for pvalues to be added to
aov_pval_list_all <- list()

final_statistics_anova_all_not_standardized <- lapply(1:ncol(processed_metabolite_values_combat_final_sample_by_metabolite_anova_all_not_standardized), function(i){
    anova_df <- data.frame(metabolite=processed_metabolite_values_combat_final_sample_by_metabolite_anova_all_not_standardized[,i], treatment_final_all)
    aov_test <- aov(metabolite ~ treatment_final_all, data=anova_df)
    aov_pval <- summary(aov_test)[[1]][["Pr(>F)"]][1]
    aov_pval_list_all[[length(aov_pval_list_all) + 1]] <- aov_pval
}) 
  
final_aov_dataframe_anova_all_not_standardized <- data.frame(colnames(processed_metabolite_values_combat_final_sample_by_metabolite_anova_all_not_standardized), unlist(final_statistics_anova_all_not_standardized))

significant_aov_dataframe_anova_all_not_standardized <- final_aov_dataframe_anova_all_not_standardized[final_aov_dataframe_anova_all_not_standardized$unlist.final_statistics_anova_all_not_standardized. < 0.05, ]

# Turn all pvalues into adjusted pvalues by applying FDR correction which multiples all values by the number of metabolites
final_aov_dataframe_with_correction_anova_all_not_standardized <- final_aov_dataframe_anova_all_not_standardized %>% dplyr::mutate(group_padj = p.adjust(final_aov_dataframe_anova_all_not_standardized$unlist.final_statistics_anova_all_not_standardized., method = 'fdr'))

significant_aov_dataframe_with_correction_anova_all_not_standardized <- final_aov_dataframe_with_correction_anova_all_not_standardized[final_aov_dataframe_with_correction_anova_all_not_standardized$group_padj < 0.05, ]
```

Below we make a boxplot for ion 736.5490

```{r}
# make dataframe with remaining ions after filtering with all data
processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized_filtered_by_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]
# Make dataframe for ggplot
dataframe_final <- data.frame(processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized_filtered_by_anova)
# Remove X from column names
names(dataframe_final) <- sub("^X", "", names(dataframe_final))
# Add column of phenotypes
dataframe_final$phenotype <- treatment_final_all
# Change name of column
colnames(dataframe_final)[colnames(dataframe_final) == "732.5503"] ="Mol %"

# Specify statistical comparisons
my_comparisons <- list(c("wt_6mo", "wt_12mo"), c("wt_12mo", "wt_22mo"))

tiff("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots For Paper/negative_hippocampus_732_5503_boxplot.tiff", units="in", width=5, height=5, res=300)

# make boxplot
ggboxplot(dataframe_final, x = "phenotype", y = 'Mol %', color = "phenotype", 
          add = "jitter", legend = "none", xlab = "") + 
  ggtitle('m/D: 732.5503 [+]') +
  theme(plot.title = element_text(hjust = 0.5)) +
  stat_compare_means(comparisons = my_comparisons, method = 't.test', symnum.args=list(cutpoints = c(0, 0.2), symbols = c("**"))) +
  scale_x_discrete(limits=c("wt_6mo", "tg_6mo", "wt_12mo", "tg_12mo", "wt_22mo", "tg_22mo"),labels=c("WT", "APPsw", "WT", "APPsw", "WT", "APPsw")) + 
      coord_cartesian(clip = 'off') +
    geom_text( size = 6, aes(x = c(1.1, 0, 0, 0, 0, 0, 3.1, 0, 0, 0, 0, 0, 5.1, 0, 0, 0, 0, 0), y = 0, label = c("6mo", "", "", "", "", "", "12mo", "", "", "", "", "", "22mo", "", "", "", "", ""),
    hjust = 0, vjust = 4)) + 
  theme(axis.title.y = element_text(color = "grey20", size = 20)) + 
  theme(axis.text.x = element_text(color = "grey20", size = 15)) + 
    theme(axis.text.y = element_text(color = "grey20", size = 15))
dev.off()
```

```{r}
# make dataframe with remaining ions after filtering with all data
processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized_filtered_by_anova <- processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized[, significant_aov_dataframe_anova_all$colnames.processed_metabolite_values_combat_final_sample_by_metabolite_anova_all.]
# Make dataframe for ggplot
dataframe_final <- data.frame(processed_metabolite_values_combat_final_sample_by_metabolite_not_standardized_filtered_by_anova)
# Remove X from column names
names(dataframe_final) <- sub("^X", "", names(dataframe_final))
# Add column of phenotypes
dataframe_final$phenotype <- treatment_final_all
# Change name of column
colnames(dataframe_final)[colnames(dataframe_final) == "871.5392"] ="Mol %"

# Specify statistical comparisons
my_comparisons <- list(c("wt_12mo", "wt_22mo"))

tiff("D:/NEW All AGE Negative masks and roi sums/Average Hippocampus/Boxplots For Paper/negative_hippocampus_871_5392_boxplot.tiff", units="in", width=5, height=5, res=300)

# make boxplot
ggboxplot(dataframe_final, x = "phenotype", y = 'Mol %', color = "phenotype", 
          add = "jitter", legend = "none", xlab = "") + 
  ggtitle('m/D: 871.5392 [+]') +
  theme(plot.title = element_text(hjust = 0.5)) +
  stat_compare_means(comparisons = my_comparisons, method = 't.test', symnum.args=list(cutpoints = c(0, 0.2), symbols = c("*"))) +
  scale_x_discrete(limits=c("wt_6mo", "tg_6mo", "wt_12mo", "tg_12mo", "wt_22mo", "tg_22mo"),labels=c("WT", "APPsw", "WT", "APPsw", "WT", "APPsw")) + 
      coord_cartesian(clip = 'off') +
    geom_text( size = 6, aes(x = c(1.1, 0, 0, 0, 0, 0, 3.1, 0, 0, 0, 0, 0, 5.1, 0, 0, 0, 0, 0), y = 0, label = c("6mo", "", "", "", "", "", "12mo", "", "", "", "", "", "22mo", "", "", "", "", ""),
    hjust = 0, vjust = 4)) + 
  theme(axis.title.y = element_text(color = "grey20", size = 20)) + 
  theme(axis.text.x = element_text(color = "grey20", size = 15)) + 
    theme(axis.text.y = element_text(color = "grey20", size = 15))
dev.off()
```
